---
title: "ses5206_1"
author: "SP + LZ"
date: "10/24/2021"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_depth: 5
    toc_float: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
```

# Research Question

How does affordable housing impact property value? Specifically for the purposes of this assignment, how does affordable housing (defined a variety of ways) affect property values in San Francisco, California, between 2013-14 and 2018-19?

# Prior Research 

TKTKTKTK

# Data

The sample population for this study is property values in San Francisco, California, in 2013-14 and 2018-19. The analysis will include the following variables: 

* 
* 
* 

## Load Data 

```{r}
sf_1314 <- read_csv("sf_tax_1314.csv") 

names(sf_1314)[1] <- 'Site'

names(sf_1314)[3] <- 'Block_Lot'

names(sf_1314)[31] <- 'LandValue_1314'

names(sf_1314)[32] <- 'PropValue_1314'

sf_1314_clean <- sf_1314 %>%
  select(Site, Block_Lot, LandValue_1314, PropValue_1314) %>%
    mutate(TotValue_1314 = PropValue_1314 + LandValue_1314)
```
```{r}
sf_1819 <- read_csv("sf_tax_1819.csv") 

names(sf_1819)[1] <- 'Site'

names(sf_1819)[2] <- 'Block_Lot'

names(sf_1819)[31] <- 'LandValue_1819'

names(sf_1819)[32] <- 'PropValue_1819'

sf_1819_clean <- sf_1819 %>%
  select(Site, Block_Lot, LandValue_1819, PropValue_1819) %>%
    mutate(TotValue_1819 = PropValue_1819 + LandValue_1819)
```
```{r}
data <- left_join(sf_1314_clean, sf_1819_clean) 

%>% 
  left_join(election) %>%
  left_join(CO_type) %>%
  left_join(covid)
```

